The controlled choice design and private paternalism in pawnshop borrowing - STATA documentation

### 2024-05-24 Restud submission/STATA_documentation.tex
new submission

%  \documentclass[oneside,11pt]{article}

% \input{preamble.tex}
% %%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
% \usepackage{xr}
% \makeatletter
% \newcommand*{\addFileDependency}[1]{
%   \typeout{(#1)}
%   \@addtofilelist{#1}
%   \IfFileExists{#1}{}{\typeout{No file #1.}}
% }
% \makeatother

% \newcommand*{\myexternaldocument}[1]{
%     \externaldocument{#1}
%     \addFileDependency{#1.tex}
%     \addFileDependency{#1.aux}
% }

% %\myexternaldocument{OA}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT
% \begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% APPENDIX 
\setcounter{table}{0}
\setcounter{figure}{0}
\setcounter{section}{0}
\pagenumbering{gobble}

\newgeometry{margin=1in}

\begin{center}
	\LARGE Supplementary Appendix for ``The controlled choice design and private paternalism in pawnshop borrowing'' \\[0.5em]
	%\Large{Appendix $-$ For Online Publication} \\[1em]
	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia}
\end{center}

\appendix
\pagenumbering{arabic}
\renewcommand\thefigure{OA-\arabic{figure}}
\renewcommand\thetable{OA-\arabic{table}}
\renewcommand*{\thepage}{OA - \arabic{page}}
\renewcommand\thesection{Appendix \Alph{section}.}
\renewcommand\thesubsection{\Alph{section}.\arabic{subsection}}

%\renewcommand{\cftparskip}{0em} % NOT NEEDED
\renewcommand\cftsecdotsep{\cftdotsep}
\renewcommand\cftsubsecdotsep{\cftnodots}
\renewcommand{\cftsecnumwidth}{6em}
 \renewcommand{\cftpnumalign}{r}
%\renewcommand{\cftsecleader}{\normalfont\cftdotfill{\cftsecdotsep}}

\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}\hspace{1.8em}}
%\renewcommand{\cftsecpagefont}{20em}
%\renewcommand{\cftfignumwidth}{6em}
%\renewcommand{\cfttabnumwidth}{3.3em}

%\tableofcontents
\etocdepthtag.toc{mtappendix}
\etocsettagdepth{mtchapter}{none}
\etocsettagdepth{mtappendix}{subsection}

\setstretch{0.9}
%\renewcommand\contentsname{} % the empty name

%\begingroup
%\let\clearpage\relax
%%\vspace{-1.5em} % the removed space. Set as appropriate
%\tableofcontents
%\endgroup

%\newpage

\linespread{1}

%\section{ Treatment Explanation Materials and Pictures}
\section{Treatment Explanation Materials} 
%\vspace{.2in}

%\subsection{Materials}

\begin{figure}[H]
     \caption{Contract Terms Summary}
    \label{PaperSlip}
    \begin{center}
    %\begin{subfigure}{0.65\textwidth}
    %\caption{Receipt for client}
     %   \centering
        \includegraphics[width=0.5\textwidth]{Figuras/TicketLenderP.png}
    %\end{subfigure}

    %\vspace{3ex}
    %\begin{subfigure}{0.65\textwidth}
    %\caption{Personal promise signed by client}
     %   \centering
    %    \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
    %\end{subfigure}
    \end{center}
    \scriptsize{
        We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity). We want to highlight the salience of some items. First the title clearly indicated which contract the client has (arrow 1). Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 2\% of the value of the monthly payment (arrow 2). Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month. %The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient. It emphasizes that the client is giving his word, and that the promise is not a legal document.
        }
\end{figure}

\begin{figure}[H]
     \caption{Explanatory Material}
    \label{ExplanatoryMaterial}
    \begin{center}
        \centering
        \includegraphics[width=0.6\textwidth]{Figuras/micas.pdf}

    \end{center}
    \scriptsize{
        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.}
\end{figure}

%\subsection{Pictures}
%
%\begin{figure}[H]
%     \caption{Some Pawnshops}
%    \label{PawnshopPicture}
%    \begin{center}
%    \begin{subfigure}{0.405\textwidth}
%    \caption{Appraiser/tellers inside a pawnshop}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
%    \end{subfigure}
%        \begin{subfigure}{0.45\textwidth}
%    \caption{Pawnshop}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
%    \end{subfigure}
%    
%        \vspace{3ex}
%
%    \begin{subfigure}{0.45\textwidth}
%    \caption{Pawnshop}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
%    \end{subfigure}
%    \begin{subfigure}{0.415\textwidth}
%    \caption{Lost pawns which are for sale}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
%    \end{subfigure}
%    \end{center}
%    \scriptsize{
%        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality.} 
%\end{figure}

%\vspace{.1in}
%\begin{figure}[H]
%     \caption{Gold buyers next to pawnshops}
%    \label{GoldBuyers}
%    \begin{center}
%    \begin{subfigure}{.49\textwidth}
%    \caption{Gold buyer next to pawnshop 1}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/empenio7_.png}
%    \end{subfigure}
%    \begin{subfigure}{.49\textwidth}
%    \caption{Gold buyer next to pawnshop 1}
%        \centering
%        \includegraphics[width=\textwidth]{Figuras/empenio8_.png}
%    \end{subfigure}
%       \vspace{3ex}
%       
%    \end{center}
%    \scriptsize{
%        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
%\end{figure}

\begin{comment}
\\
\begin{table}[H]
\caption{Number of pawns balance before and after the experiment}
\label{num_pawns_bal}
\begin{center}
\scriptsize{\input{./Tables/num_pawns_bal.tex}}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{num\_pawns\_bal.do}
\end{table}
\end{comment}
%\todo[inline]{removed}

\newpage
\subsection{Survey}   \label{app:survey_data}

\normalsize
\linespread{1.05}
%Really force it to normal size and linespread
\normalsize
\linespread{1.05}

\begin{table}[H]
\caption{Baseline survey questions (translated to English)}
\label{baseline_survey}
\begin{center}
\scriptsize{\input{./Tables/transcribed.tex}}
\end{center}
\scriptsize{
Translation of the baseline questionnaire.}
\end{table}

\newpage

We now present analysis of the extent to which the survey-responding sample is representative and balanced.
Table \ref{SS_cond_survey} presents information about survey non-response.
Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to at least one survey question.
The p-values in the fourth column are for the F-test of no difference of means across treatment arms. 
Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rates across treatment arms. 
This panel uses data from participants who answered at least one survey question and went on to pawn on the same day as their survey response.
From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are likewise stable across treatment arms.
Table \ref{TUT_cond_survey} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
In each row, column (1) presents the full-sample TUT estimate and standard error while the remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex. 
As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
In exercises that rely on a single survey question, we use data for every borrower who answered that question.
In the random forest exercises described below, we use data for every borrower who answered at least one survey question.

%\newpage
\subsection{More descriptives}

%The second thing to note is that those that are not closed at the end of our sample period have already incurred substantial financial cost, even though they have not defaulted yet.

%Of those who renew, 83\% lose the pawn. Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn. Panel (b) normalizes the cost by loan size. It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn. For them the cost is between 140\% and 250\% of the loan value. %{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}

\begin{figure}[!h]
\caption{Financial cost.}
  \label{fc_hist}
    \begin{center}
    \begin{subfigure}{.42\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
        \caption{}
    \end{subfigure}
     \begin{subfigure}{0.42\textwidth}
       \centering
      \includegraphics[width=\textwidth]{Figuras/hist_apr.pdf}
      \caption{}
    \end{subfigure}
    \end{center}

 \scriptsize{Panel (a) plots a histogram of this financial cost in pesos for all loans in the experiment, stratified by whether we observed that they ended in default or recovery of the pawn. Panel (b) shows the analogous histogram for the APR.
%defaulted (44\%), recovered their pawn (43\%), or whether they are censored in our data (13\%). 
We see that borrowers who default incur higher costs; part of this is mechanical as losing their collateral is part of the cost. Most of the APR costs indeed come from clients who do not recover their pawn.}

      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
\end{figure}

\begin{figure}[!h]
    \caption{Behavior of borrowers who lost their pawn}
    \label{proxy_naive}
    \begin{center}
    \begin{subfigure}{0.35\textwidth}
        \caption{Elapsed days to first payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \caption{Elapsed days to last payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
    \end{subfigure}
        \begin{subfigure}{0.35\textwidth}
        \caption{Payments as \% of loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
    \end{subfigure}
    \end{center}
        \scriptsize 
        This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn. Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment. Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan. This amounts to starting a new loan with the same conditions and same pawn. Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.
      %\textit{Do file: }  \texttt{hist\_den\_default.do}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{ Internal Validity}

If potential borrowers disliked being forced into a commitment contract, we would expect a lower number of pawns on branch days where only the commitment contract is available compared to control days. Table \ref{attrition_table} shows that this is not the case. There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day. Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability. Differences across arms are smaller when for medians, or when we compare the number of borrowers pawning (some borrowers pawn more than one piece). Figure \ref{boxplot_attrition} shows that distribution of loans per day is comparable across arms. The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns becomes identical across arms.}

\begin{table}
\caption{Limited and balanced attrition}
\label{attrition_table}
\begin{center}
\scriptsize{\input{./Tables/Attrition.tex}}
\end{center}
\scriptsize{Each row in this table 
 corresponds to a regression. The dependent variables are: the number of pawns-loans originated per day per branch, the number of borrowers per day-branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey. Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice). The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients. Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.}
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status. We find that in no arm did more than three percent of individuals who responded to the survey go on to refuse loans. That is, the overwhelming marjority of potential borrowers did not leave the branch after learning which contract was on offer. Moreover, the extremely small fraction that did leave is balanced across arms.  Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.

A less critical form of attrition is differential refusal to answer the survey questions.  The survey was conducted before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.  Our core experimental estimates do not use the survey data as covariates, but the analysis in Section \ref{Paternalism} is restricted to the subset of borrowers who answered at least some survey questions. The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 78 percent).

\begin{figure}[H]
     \caption{Box-plot across arms}
    \label{boxplot_attrition}
    \begin{center}
    \begin{subfigure}{0.35\textwidth}
    \caption{Number of pawns}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
        \begin{subfigure}{0.35\textwidth}
    \caption{Number of borrowers}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        This figure presents box-plot for the number of pawns and borrowers per branch-day across different arms. The solid black line represent the median, while the gray line represent the mean. The blue dots represent an implicit CDF. 
\end{figure}

% \begin{figure}[H]
%      \caption{Number of pawns and borrowers before and after the experiment}
%     \label{line_pawns_before_after}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/after_before_bal.pdf}
%     \scriptsize
%         This figure shows the number of pawns and borrowers before, during, and after the experiment for the different branches.
% \end{figure}

% \begin{figure}[H]
%      \caption{No discontinuity in the number of pawns before and after experiment}
%     \label{rd_pawns}
%        \begin{center}
%     \begin{subfigure}{0.45\textwidth}
%     \caption{Number of pawns - before}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/rd_before_pawns.pdf}
%     \end{subfigure}
%         \begin{subfigure}{0.45\textwidth}
%     \caption{Number of pawns - after}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/rd_after_pawns.pdf}
%     \end{subfigure}
%      \begin{subfigure}{0.42\textwidth}
%     \caption{Number of borrowers - before}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/rd_before_borr.pdf}
%     \end{subfigure}
%         \begin{subfigure}{0.45\textwidth}
%     \caption{Number of borrowers - after}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/rd_after_borr.pdf}
%     \end{subfigure}
%     \end{center}
%     \scriptsize
%         This figure shows the number of pawns and borrowers before, during, and after the experiment for the different branches.
% \end{figure}

\vspace{-1em}

\begin{table}[H]
\caption{Balance conditional on survey response and question-by-question response rates} %by treatment arm}
\label{SS_cond_survey}
\begin{center}
\scriptsize{\input{./Tables/SS_cond_survey.tex}}
\end{center}
\scriptsize

Panel A of this table presents the same information as Panel A of Table \ref{SS}, restricted to the subsample of borrowers who answered at least one survey question. Conditional on survey response, loan amount and weekday are balanced across arms. Panel B presents response rates to each survey question across arms, along with p-values for the F-test of no difference in response rates across arms, using data for borrowers who pawned on the same day as their survey response. 
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

\begin{landscape}
\begin{table}[H]
\caption{Survey Non-response: TUT estimates for respondents to each survey question.}
\label{TUT_cond_survey}
\begin{center}
\scriptsize{\input{./Tables/tut_cond_survey.tex}}
\end{center}
\scriptsize

Some borrowers did not respond to our survey; others only completed part of the survey.
This table computes the TUT effect for a number of sub-groups by survey response, and compares them against the overall TUT effect.
The top panel uses financial cost as the outcome variable, while the bottom panel uses APR.
Each group is defined by the borrowers who responded to a particular \emph{subset} of the survey questions. 
For example, column (4) computes TUT effects for the subgroup of borrowers who responded to the two questions needed to compute our measure of present bias, while column (8) computes the TUT for the subgroup of borrowers who provided their age.
The bottom row of the table counts the number of borrowers in each category.
TUT estimates are quite stable across sub-groups and generally similar to the full-sample estimates.
Because standard errors increase as sample size falls, some of the sub-group estimates are not statistically significant.
%\textit{Do file: } \texttt{tut_cond_survey.do}
\end{table}
\end{landscape}

\newpage

\section{ Main treatment effects: Additional material}

%\begin{landscape}
%\subsection{Multiple loans}
%
%\begin{table}[H]
%\caption{Multiple-loans robustness check}
%\label{multiple_loans}
%\begin{center}
%\scriptsize{\input{./Tables/multiple_loans.tex}}
%\end{center}
% \scriptsize
% An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.  43\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.  The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure (ITT) \citep{cullen2006effect, abdulkadirouglu2011accountability}.\\
% 
% This table provides robustness for our main results for different ways to handling the multiplicity of loans. Columns 1-4 repeat the main analysis of financial cost and APR using the baseline approach from our main results,i.e. it only considers the first visit, while allowing multiple loans for the same-day. Columns 5-8 considers all loans including dummies for the order of pawns for an individual, essentially making the identification within-order.  Columns 9-12 pursue the ITT strategy of always assigning the first treatment status to all subsequent pawns. The core treatment effects are robust to any of these ways of handling repeat pawning.  
% 
%%\textit{Do file: } \texttt{multiple\_loans.do}
%\end{table}
%
%
%\end{landscape}

\begin{figure}[H]
    \caption{Determinants of choice}
    \label{determinants_choose}
    \begin{center}
    \begin{subfigure}{0.6\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
    \end{subfigure}
    \end{center}
      \scriptsize

      The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment. Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm. 
%\textit{Do file: } \texttt{determinants_choice.do}       
\end{figure}

\begin{figure}[H]
    \caption{Histogram of payments}
    \label{hist_payments}
    \begin{center}
    \begin{subfigure}{0.31\textwidth}
        \caption{Status-quo}
        \centering
    \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
    \end{subfigure}
    \begin{subfigure}{0.31\textwidth}
        \caption{Forced commitment}
        \centering
    \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
    \end{subfigure}
    \begin{subfigure}{0.31\textwidth}
        \caption{Choice commitment}
        \centering
    \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
    \end{subfigure}    
    \end{center}
     \scriptsize
     This figure shows the schedule of payments for each treatment arm. In other words it records the time after the loan origination when the borrower makes a payment toward recovery of the pawn. We can see that for both the Forced commitment and Choice commitment arm, payments are bunching at the 30 and 60 days, while most payments are done around the due date of the loan (90 days).

      %\footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
\end{figure}

\subsection{Censoring} \label{App_censoring}

\normalsize
\linespread{1.05}
%Really force it to normal size and linespread
\normalsize
\linespread{1.05}

Some loans in our sample are ``censored'' in that they continue beyond our observation period.
For these loans, we do not know whether the borrower ultimately defaulted or recovered her pawn.
In this appendix, we show that our main results are robust to different ways of addressing censoring.

Our main results, presented above, make no assumption on the default/recovery status of this loans. However, we compute the Financial Cost \& APR considering all the payments done so far. We now consider some alternative approaches.

One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.  In Table \ref{bounding_censoring} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.  Panel A assumes all censored loans are repaid, and Panel D that all default. Because forced commitment causes borrowers to make payments earlier than they otherwise would have, In Panel A we make a conservative assumption. To see why, suppose for the sake of argument that commitment affects payment timing, but does not not default.
In other words, suppose that treatment makes censoring \emph{less likely} but has no effect on uncensored outcomes. 
If we were to treat all outstanding loans as defaults--the opposite of our convention--this would artificially inflate the rate of default among control loans relative to treatment loans.

Panel B provides the lower bound for the treatment effect by assuming censored control loans are always repaid and treatment loans never are, and Panel C the upper bound by making the reverse assumption.  Comfortingly, even with these extreme assumptions the significance on the main treatment effects never flips and treatment effects on financial cost and interests payments remain negative and significant in all scenarios.  So there appears to be no scope for the censoring issue to overturn our main results.

Finally, Panel E of this table conducts a lasso logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.  This is a best guess of the outcome on censored loans.  Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -204 (main results) to -264 (censored loans predicted), and the APR from -11\% to -17\%.  Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.

\begin{table}[H]
\caption{Bounding censoring} 
\label{bounding_censoring}
\begin{center}
\resizebox{1.0\textwidth}{!}{
\scriptsize{\input{./Tables/censoring_imp_1.tex}}
}
\end{center}

\end{table}
\begin{table}[H]
\begin{center}
\resizebox{1.0\textwidth}{!}{
\scriptsize{\input{./Tables/censoring_imp_2.tex}}
}
\end{center}

 \scriptsize {
 Given the censored loans, i.e. loans that have not finished by the end of the observation period, we estimate `a la Manski' bounds for these loans, meaning that we impute all loans to either \emph{default}$=1$ or \emph{recovery}$=0$ depending on the treatment arm. Different panels perform different imputations for the censored loans for all possible combinations for the imputation, and computes the ATE for the same outcomes of Table \ref{main_impact_table}. Panel A, for instance, assumes that all outstanding loans are fully payed. Panel B is the most conservative imputation since it assumes all outstanding loans in the control arm are payed, while all the outstanding loans in the forced commitment arm default. Panel C, on the other hand, is the most optimistic scenario opposite to that of Panel B. Panel D assumes all remaining loans default. The last panel makes the imputation to the censored loans according to the best prediction using a piecewise lasso logit model for default. In concrete, we build two logit models with lasso regularization, depending whether the loan duration is less than 220 days (two cycles) or more than 220 days. For prediction we use the former whenever the last recorded payment was done within 220 days, and the latter otherwise. Both models includes loan characteristics (loan size, branch), and payment behavior (loan duration so far, days to first payment, \% of first payment, \% of payments at 30, 60, 90, and 105 days, and \% of interest payed at 105 days), but the latter model also includes \% of payments at 150, 180, and 210 days. This predictive model achieves an accuracy rate of 92\% both in-sample and out-of-sample.

\noindent Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome. }
\end{table}

\begin{figure}[H]
        \caption{Interpolation on bounding censoring for Default}
        \vspace{-1em}
    \label{interpolation_censoring_imp}
    \begin{center}
   % \begin{subfigure}{0.49\textwidth}
   % \caption{Significance area for APR}
   %      \centering
   %      \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
   %  \end{subfigure}     
   %  \begin{subfigure}{0.49\textwidth}
   % \caption{Significance area for Default }
        \centering
        \includegraphics[width=0.5\textwidth]{Figuras/frontera_sig_def_imp.pdf}
    % \end{subfigure} 
    \end{center}
    \vspace{-1em}
     \scriptsize  {The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
     This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment. Each corner in the square will correspond to one of the panels from the Table \ref{bounding_censoring}. For instance, the origin is the best-case scenario (Panel C) and the point (100,100) (Panel B) is the worst-case scenario. Thus we can think of this graph as an `interpolation' from the four extreme cases. The `x' indicates the proportions imputed by the lasso logit model, and the different lines correspond to setting different significance levels. We do not include the plot for APR nor financial cost, since for any imputation we still have significant results.}

     %\textit{Do file: }  \texttt{interpolation_censoring_imp.do}
\end{figure}

\begin{figure}[H]
        \caption{Survival graph}
        \vspace{-2em}
    \label{survival_graph}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Ended contract}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
   \caption{Recovery}
        \centering
        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
    \end{subfigure}     
    \end{center}
    \vspace{-1em}
     \scriptsize  This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.
     %\textit{Do file: }  \texttt{survival\_graph.do}
\end{figure}

\begin{figure}[H]
        \caption{\% of payment over time}
        \vspace{-2em}
    \label{porc_payment_over_time}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
        \caption{Unconditional}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
        \caption{Conditional on default}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time_default.pdf}
    \end{subfigure}     
    \end{center}
     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
     %\textit{Do file: }  \texttt{cumulative\_porc\_pay\_time.do}
\end{figure}

\subsection{Robustness accounting for other costs}

\begin{table}[!h]
\caption{Effects on more comprehensive cost measures}
\label{table_robustness_fc}
\begin{center}
\scriptsize{\input{./Tables/fc_robustness.tex}}
\end{center}
 \scriptsize{ This table augments the measure of financial cost presented in Table \ref{main_impact_table} with measures of transaction costs, subjective costs, and adjustments for liquidity costs. Panel A reports financial cost in pesos, while Panel B shows APR. Columns (1) and (6) replicate our previous results for comparability. Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value. Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of visits that each individual made.\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.} Columns (4) and (9) adjust to consider the liquidity cost. Finally, columns (5) and (10) include all three changes together. The main takeaway from the table is that results are quite robust to including a much expanded measure of costs. Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
%\textit{Do file: } \texttt{fc\_robustness.do}
\end{table}

\section{ Alternative explanations}

\subsection{Learning}
\normalsize
Table \ref{learning_table} presents information about borrowers' \emph{future} pawning behavior as a function of treatment assignment. Column (1) considers the 228 clients who returned only a second time to pawn again at a day/branch that was randomly assigned to the choice arm. Each of the two rows in this column presents a difference of mean commitment take-up rates, and associated standard error. The first row compares those who were \emph{initially} assigned to forced commitment against those where were assigned to control; the second row compares those who were initially assigned to the choice commitment arm to those who were assigned to the other two arms. In each case, there is no statistically discernible difference in the rates of commitment take-up. Granted, this is a selected sample because the decision to pawn again is potentially endogenous to the initial treatment allocation. For this reason, Column (2) considers the full sample of 4441 borrowers by re-defining the outcome variable to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment. This composite outcome variable is not subject to the sample selection problem (although it is directly driven by the decision to repeat borrow). The comparison in the two rows remains the same: forced commitment versus control in row one and choice commitment versus forced arms in row two. Again, there is no statistically discernible difference in commitment take-up rates in either row. While these exercises cannot completely exclude the possibility that learning plays a role, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.

\vspace{.1in}
\begin{table}[!h]
        \caption{Effect of Prior Assignment on Subsequent Choice}
    \label{learning_table}
\begin{center}
\scriptsize{\input{./Tables/learning_exp.tex}}
\end{center}
 \scriptsize

Column (1) reports results for the 228 borrowers who returned to pawn again at a day/branch that was randomly assigned to the choice arm, enabling us to observe whether they chose commitment or the status quo contract.
Each row presents a difference in mean commitment take-up rates and associated standard errors.
The first row (ATE) compares borrowers who were initially assigned to forced commitment against those were assigned to the control condition.
The second row (ITT) compares borrowers who were initially assigned to the choice commitment condition to those who were not.
Whereas column (1) conditions on the (endogenously) selected sample of borrowers who return to pawn again, column (2) considers the full sample by re-defining the ``outcome'' to be an indicator for whether a borrower pawned again on a day when choice was offered \emph{and} chose commitment.

%This table explores learning by focusing on a subsample of borrowers in the experiment and observing their subsequent behavior. Column 1 conditions the sample on borrowers who (a) pawned during the experiment a subsequent time after being assigned to control, forced commitment or choice (the regressors), and (b) when pawning again they went to a branch day when (randomly) choice was available, thus enabling us to observe if they chose the commitment contract or the status quo.  in this sample it estimates a linear probability model where the dependent variable is equal to one if the borrower chose the commitment contract in that subsequent `choice' occasion and zero otherwise. The regressors are indicators for the treatment arms in their first pawn in the experiment. Column 1 conditions the sample on the (endogenous) event of pawning again. Column 2 does not condition the sample, but instead defined the dependent variable as equal to one \hl{if the borrower pawned subsequently and choice was available that day and chose commitment, and zero otherwise.}

\end{table}

\subsection{Discount rates}

>>>>

\documentclass[11pt, a4paper]{article}

\input{preamble.tex}
%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{
    \externaldocument{#1}
    \addFileDependency{#1.tex}
    \addFileDependency{#1.aux}
}

\newgeometry{margin=1in}
\linespread{1.25}
\begin{document}

\title{The controlled choice design and private paternalism in pawnshop borrowing - STATA documentation}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{}
\maketitle
